New lower bounds for Schur and weak Schur numbers

### 2021-04-09 article/weakschur.tex
correction

\begin{definition}
Let \( (k,b) \in (\mathbb{N}^*)^2\). If there exist \(p\) such that exists a partition of \([\![1, p]\!]\) into \(k\)
subsets which is a \(b\)-WS-template of \(k\) colors and lenght \(p\), we note:
\\\\\(WS_b^+=\max \{p\in \mathbb{N}^*\)/ there exists a partition of \([\![1, p]\!]\) into \(k\) subsets which is a
\(b\)-WSF-template of \(k\) colors and lenght \(p\) \}
\\\\
If this \(p\) does not exist, we set \(WS_b^+= 0\)
\end{definition}

@@

\begin{theorem}
Let \((p,k,b) \in (\mathbb{N}^*)^3\), let \( (q,n) \in (\mathbb{N}^*)^2\). If there exists a partition of \(n\)
sum-free subsets of \([\![1,q]\!]\) and a partition of k subsets \((A_1,....,A_k)\) of \([\![1, p]\!]\) which is a
\(b\)-WSF of \(k\) colors and lenght \(p\),
 then there exists a partition of \([\![1, b+q \times p]\!]\) into \((k+n-1)\) weakly sum-free subsets.
\end{theorem}

In particular, if we choose \(q = S(n)\) and \(p = WS^+(k)\) in the last theorem, the next corollary follows.

\begin{corollary}
\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } let ~ b_{max}=max \{b\in \mathbb{N}^*/WS^+(k+1)=WS_b^+(k+1)\},\) \[
WS(n+k) \geqslant S(n) WS^+(k+1)+b_{max}\]
\end{corollary}

>>>>

\begin{definition}
Let \( (k,b) \in (\mathbb{N}^*)^2\). If there exist \(p\) such that exists a partition of \([\![1, p]\!]\) into \(k\)
subsets which is a \(b\)-WS-template of \(k\) colors and lenght \(p\), we note:
\\\\\(WS_b^+=-b+\max \{p\in \mathbb{N}^*\)/ there exists a partition of \([\![1, p]\!]\) into \(k\) subsets which is a
\(b\)-WSF-template of \(k\) colors and lenght \(p\) \}
\\\\
If this \(p\) does not exist, we set \(WS_b^+= 0\)
\end{definition}

@@

\begin{theorem}
Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \(k\)
sum-free subsets of \([\![1,p]\!]\) and a partition of n subsets \((A_1,....,A_n)\) of \([\![1, q]\!]\) which is a
\(b\)-WSF of \(n\) colors and lenght \(q\),
 then there exists a partition of \([\![1, b+q \times (p-b)]\!]\) into \((k+n-1)\) weakly sum-free subsets.
\end{theorem}

In particular, if we choose \(p = S(k)\) and \(q = WS^+(n)\) in the last theorem, the next corollary follows.

\begin{corollary}
\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } let ~ b_{max}=max \{b\in \mathbb{N}^*/WS^+(n+1)=WS_b^+(n+1)\},\) \[
WS(n+k) \geqslant S(k) WS^+(n+1)+b_{max}\]
\end{corollary}
